Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-11-10 manuscript.tex
We got a DOI at PLOS ONE [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/f1c96b127bb47e033309ae3205b2ddf5f0210582.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/f1c96b127bb47e033309ae3205b2ddf5f0210582/checks
https://github.com/habi/acinar-analysis-manuscript/runs/1443174505

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been accepted for publication in \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...f456264a8870c9b4324894a3ec64a04fcf8280f3}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/f456264a8870c9b4324894a3ec64a04fcf8280f3/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/f456264a8870c9b4324894a3ec64a04fcf8280f3}{habi/acinar-analysis-manuscript@f456264}
on September 24, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(f456264)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(f456264)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

>>>>

\emph{This manuscript is published in PLOS ONE at \url{https://doi.org/10.1371/journal.pone.0257349}.}

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/f1c96b127bb47e033309ae3205b2ddf5f0210582/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/f1c96b127bb47e033309ae3205b2ddf5f0210582}{habi/acinar-analysis-manuscript@f1c96b1}
on November 10, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(f1c96b1)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(f1c96b1)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}
